---
title: "Vaccine solidarity replication"
author:
  - Ferdinand Geißler
  - Felix Hartmann
  - Macartan Humphreys
  - Heike Klüver
  - Johannes Giesecke
date: last-modified
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: false
    code-tools: true
    include-in-header:
      text: |
        <style>
        details.replication-source {
          margin: 0.75rem 0 1.5rem;
          padding: 0.85rem 1rem 1rem;
          border: none;
          border-radius: 0.4rem;
          background: #1a5f9e;
          color: #ffffff;
          font-size: 0.92em;
          box-shadow: 0 2px 10px rgba(26, 95, 158, 0.28);
        }
        details.replication-source > summary {
          cursor: pointer;
          font-weight: 600;
          color: #ffffff;
          list-style: none;
          padding: 0.15rem 0;
        }
        details.replication-source > summary:hover {
          color: #e3f2fd;
        }
        details.replication-source > summary::-webkit-details-marker {
          display: none;
        }
        details.replication-source > summary::before {
          content: "▸ ";
          display: inline-block;
          transition: transform 0.15s ease;
        }
        details.replication-source[open] > summary::before {
          transform: rotate(90deg);
        }
        details.replication-source .source-file {
          margin: 0.5rem 0 0;
          font-size: 0.85em;
          color: #c5dff5;
        }
        details.replication-source .source-file code {
          color: #ffffff;
          background: rgba(255, 255, 255, 0.18);
          padding: 0.1em 0.35em;
          border-radius: 0.2rem;
        }
        details.replication-source div.sourceCode,
        details.replication-source pre {
          background: rgba(0, 0, 0, 0.22);
          border: 1px solid rgba(255, 255, 255, 0.22);
          border-radius: 0.3rem;
          margin-top: 0.75rem;
        }
        details.replication-source div.sourceCode pre {
          background: transparent;
          border: none;
          margin-top: 0;
        }
        details.replication-source pre,
        details.replication-source pre code,
        details.replication-source code {
          color: #f4f8fc;
        }
        </style>
execute:
  echo: true
  warning: false
  message: false
  cache: true
---

This document reproduces the main tables and figures from the original
[`analysis.Rmd`](https://github.com/wzb-ipi/vaccine_solidarity/blob/main/analysis.Rmd)
by calling the package's exported `make_*` and `format_*` functions (the same
code path as `run_replication()`).


So when a chunk calls `make_figure_1(wave4_conjoint)`

The same outputs are available as one-liners (useful for tests and Shiny):

The tables and figures are generated by using the functions that are defined in the replication package. e.g. 

* `make_table_1(wave4_conjoint)`
* `make_figure_1(wave4_conjoint)`

But these also play nicely with functions in `replicate_everything` and so one could also run: 

* `run_replication("fig_1")`
* `run_replication("tab_1")`

The rest of the file runs these functions for each figure and table and also displays the underlying code.


# Setup

```{r}
#| label: setup

library(rep1371journalpone0278337)
library(dplyr)
library(ggplot2)
library(egg)
library(estimatr)
library(bbmle)
library(broom)
library(modelsummary)
library(kableExtra)

# Set TRUE to fit tables live on render (~minutes). FALSE uses precomputed
# artifacts from build_report() (fast; default for pkgdown).
re_run_slow_analyses <- FALSE

ns <- asNamespace("rep1371journalpone0278337")
show_table_artifact <- ns$show_table_artifact
clean_replication_source <- ns$clean_replication_source
show_make_source <- ns$show_make_source
```

# Data

Data is drawn from the package

```{r}
data(wave4_conjoint, package = "rep1371journalpone0278337")
data(wave2_survey, package = "rep1371journalpone0278337")
data(vignette_labels, package = "rep1371journalpone0278337")
```

The source repository rebuilds `df_4` and `df_2` from raw CSV exports. This
package ships prepared **`wave4_conjoint`**, **`wave2_survey`**, and
**`vignette_labels`**. Rebuild from raw data with `prep_data()` when needed.

```{r}
#| label: data-check
#| echo: false

list(
  wave4_rows = nrow(wave4_conjoint),
  wave2_rows = nrow(wave2_survey)
)
```

# Analysis: main results

## Figure 1: Distribution of support for contributions of different sizes

Implementation: `R/make_figure_1.R`

```{r}
#| label: fig-1
#| fig-cap: "Figure 1. Distribution of support for contributions of different sizes."
#| fig-width: 10
#| fig-height: 6
#| code-fold: false

wave4_conjoint |>
  make_figure_1() |>
  format_figure_1()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_1")
```

</details>

## Figure 2: Marginal effects of conditions

Implementation: `R/make_figure_2.R`

```{r}
#| label: fig-2-stats
#| echo: false

df_4 <- wave4_conjoint
```

The average proposal is **`r round(mean(df_4$cash_billions, na.rm = TRUE), 2)`**
billion Euros and **`r round(mean(df_4$doses, na.rm = TRUE), 2)`** million doses.
The median proposal is **`r round(median(df_4$cash_billions, na.rm = TRUE), 2)`**
billion Euros and **`r round(median(df_4$doses, na.rm = TRUE), 2)`** million doses.

```{r}
#| label: fig-2
#| fig-cap: "Figure 2. Marginal effects of conditions."
#| fig-width: 7
#| fig-height: 3.5
#| code-fold: false

wave4_conjoint |>
  make_figure_2() |>
  format_figure_2()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_2")
```

</details>

## Figure 3: Effect of video treatment on individual solidarity

Implementation: `R/make_figure_3.R`

```{r}
#| label: fig-3
#| fig-cap: "Figure 3. Effect of video treatment on individual solidarity."
#| fig-width: 7
#| fig-height: 3.5
#| code-fold: false

wave2_survey |>
  make_figure_3() |>
  format_figure_3()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_3")
```

</details>

# Additional Results

## Figure 4: Levels of support by party

Implementation: `R/make_figure_4.R`

```{r}
#| label: fig-4
#| fig-cap: "Figure 4. Levels of support by party."
#| fig-width: 8
#| fig-height: 5
#| code-fold: false

wave4_conjoint |>
  make_figure_4() |>
  format_figure_4()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_4")
```

</details>

## Figure 5: Levels of support by migration background

Implementation: `R/make_figure_5.R`

```{r}
#| label: fig-5
#| fig-cap: "Figure 5. Levels of support by migration background."
#| fig-width: 8
#| fig-height: 5
#| code-fold: false

wave4_conjoint |>
  make_figure_5() |>
  format_figure_5()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_5")
```

</details>

## Figure 6: Marginal effects of conditions by party

Implementation: `R/make_figure_6.R`

```{r}
#| label: fig-6
#| fig-cap: "Figure 6. Marginal effects of conditions by party."
#| fig-width: 9
#| fig-height: 7
#| code-fold: false

wave4_conjoint |>
  make_figure_6() |>
  format_figure_6()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_6")
```

</details>

## Figure 7: Marginal effects of conditions by migration background

Implementation: `R/make_figure_7.R`

```{r}
#| label: fig-7
#| fig-cap: "Figure 7. Marginal effects of conditions by migration background."
#| fig-width: 9
#| fig-height: 4
#| code-fold: false

wave4_conjoint |>
  make_figure_7() |>
  format_figure_7()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_7")
```

</details>

## Figure 8: Results refreshment sample

Implementation: `R/make_figure_8.R`

```{r}
#| label: fig-8
#| fig-cap: "Figure 8. Results refreshment sample."
#| fig-width: 9
#| fig-height: 4
#| code-fold: false

wave4_conjoint |>
  make_figure_8() |>
  format_figure_8()
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_figure_8")
```

</details>

## Table 1: Structural analysis

Implementation: `R/make_table_1.R`

We assume

$$u = (a + bT + cR) \log(Y + x) - x^2 - g(x - ky)^2$$

where $T$ is trading importance, $R$ is health risk, $Y$ is total amount given by
other countries, and $y$ is average amount given by other countries. The fit is
slow (~1–2 minutes). With `re_run_slow_analyses <- FALSE` (default), the table
below loads a precomputed artifact; set the switch to `TRUE` in **Setup** to run
live on render.

```{r}
#| label: tab-1
#| eval: !expr re_run_slow_analyses
#| code-fold: !expr (re_run_slow_analyses == FALSE)
#| results: asis

wave4_conjoint |>
  make_table_1() |>
  format_table_1() |>
  knitr::asis_output()
```

```{r}
#| label: tab-1-display
#| echo: false
#| eval: !expr (re_run_slow_analyses == FALSE)

show_table_artifact("tab_1")
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_table_1")
```

</details>

## Table 2: Wave 2 conjoint (additional analyses)

Implementation: `R/make_table_2.R`

```{r}
#| label: tab-2
#| eval: !expr re_run_slow_analyses
#| code-fold: !expr (re_run_slow_analyses == FALSE)
#| results: asis

make_table_2(wave2_survey, vignette_labels) |>
  format_table_2() |>
  knitr::asis_output()
```

```{r}
#| label: tab-2-display
#| echo: false
#| eval: !expr (re_run_slow_analyses == FALSE)

show_table_artifact("tab_2")
```

<details class="replication-source">
<summary>Show underlying code</summary>

```{r}
#| echo: false
#| results: asis

show_make_source("make_table_2")
```

</details>


# Session info

```{r}
#| label: session-info

sessionInfo()
```
